On the combination of Set Functions and Failures

### 2013-07-25 docs/src/usage.tex
Default search strategy changed to breadth-first search.

\item[\fbox{\code{prdfs }}]\pindex{prdfs}
Set the search mode to evaluate non-deterministic expressions
to primitive depth-first search (which is usually the fastest method
to print all non-deterministic values).

\item[\fbox{\code{dfs}}]\pindex{dfs}
Set the search mode to evaluate non-deterministic expressions
to depth-first search. Usually, all non-deterministic values
are printed with a depth-first strategy, but one can also
print only the first value or all values by interactively requesting them
(see below for these options).

\item[\fbox{\code{bfs}}]\pindex{bfs}
Similarly to \code{dfs} but use a breadth-first search strategy
to compute and print the values of the given expression.

\item[\fbox{\code{ids}}]\pindex{ids}
Similarly to \code{dfs} but use an iterative-deepening strategy
to compute and print the values of the initial expression.
The initial depth bound is 100 and the depth-bound is
doubled after each iteration.

@@

\item[\fbox{\code{par}}]\pindex{par}
Similarly to \code{dfs} but use a parallel search strategy
to compute and print the values of the initial expression.
The system chooses an appropriate number
of threads according the current number of available processors.

@@

>>>>

\item[\fbox{\code{bfs}}]\pindex{bfs}
Set the search mode to evaluate non-deterministic expressions
to breadth-first search.
This is the default search strategy.
Usually, all non-deterministic values
are enumerated and printed with a breadth-first strategy, but one can also
print only the first value or all values by interactively requesting them
(see below for these options).

\item[\fbox{\code{dfs}}]\pindex{dfs}
Similarly to \code{bfs} but use a depth-first search strategy
to compute and print the values of the initial expression.

\item[\fbox{\code{ids}}]\pindex{ids}
Similarly to \code{bfs} but use an iterative-deepening strategy
to compute and print the values of the initial expression.
The initial depth bound is 100 and the depth-bound is
doubled after each iteration.

@@

\item[\fbox{\code{par}}]\pindex{par}
Similarly to \code{bfs} but use a parallel search strategy
to compute and print the values of the initial expression.
The system chooses an appropriate number
of threads according the current number of available processors.

@@

\item[\fbox{\code{prdfs }}]\pindex{prdfs}
Set the search mode to evaluate non-deterministic expressions
to primitive depth-first search. This is usually the fastest method
to print \emph{all} non-deterministic values.
However, it does not support the evaluation of values
by interactively requesting them.
